\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 TPDP2018/poster/main.tex
update poster

\begin{itemize}
  \item[-] $\betaset$ is the set of candidates, defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.

@@

  \item[-] $S(\dataobs)$, the smooth sensitivity\cite{nissim2007smooth}:
  $
  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}
  $,
  where:
  \begin{itemize}
   \item $d$: Hamming distance between two data sets,

   \item $LS(\dataobs')$, local sensitivity at $\dataobs'$:
   $
   LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
   $,

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] \textbf{Green}: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] \textbf{Red}: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] \textbf{Blue}: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10,000$ times under each data size or prior configuration.

>>>>

\begin{itemize}
  \item[-] $\betaset$: the set of candidates defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.

@@

  \item[-] $S(\dataobs)$ is the smooth sensitivity\cite{nissim2007smooth}:
  $
  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}
  $,
  where:
  \begin{itemize}
   \item $d$ denotes the Hamming distance between two data sets,

   \item $LS(\dataobs')$ is local sensitivity at $\dataobs'$:
   $
   LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
   $,

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] \textbf{Green}: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] \textbf{Red}: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] \textbf{Blue}: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling $10000$ times under each data size or prior configuration.
